Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2020-12-14 manuscript/draft_rsfmri.Rmd
adopted to new folder structure and Wild bootstrapping

# [ ] Evaluate SPM model comparison (more activation in SPM..)
# [ ] Discussion
# [ ] hervorheben, was von Präregistrierung abweicht
# [ ] brain images mit nilearn plotting tools einbinden
# [ ] Upload auf Neurovolt, cf. cobidas reporting guidelines
# [ ] re-do analysis with new sample 
# [ ] repeat analysis with exclusion of 10% of worst data

@@

dfw <- tidyr::pivot_wider(data = final,
                          id_cols = c("subj.ID","condition","Sex","Age_BL"),
                          names_from = "tp",
                          values_from = c("BMI","logmFD"))
```
```{r tabsample, echo=FALSE}
tab_sample <-
  knitr::kable(
    tab_sample,
    row.names = TRUE,
    format = "latex",
    booktabs = T,
    caption = "Distribution of data points at months after intervention")
tab_sample
```

@@

# table for descriptive statistics
descr <- psych::describeBy(dfw[,5:ncol(dfw)], group=dfw$condition,mat=T)
descr$predictor <- c(rep("BMI",6),rep("logmFD",6))
descr$tp <- car::recode(descr$vars, "c(1,4)='fu2';c(2,5)='fu';c(3,6)='bl'")
descr$group <- descr$group1
descr <- descr[,c("predictor","tp","group","n","mean","sd")]
descr <- descr[with(descr, order(predictor, tp)),]
descr[,c("mean","sd")] <- round(descr[,c("mean","sd")],2)
descr[c(2:6,8:12),"predictor"] <- ""
descr[c(2,4,6,8,10,12),"tp"] <- ""
rownames(descr) <- NULL

@@

ID <- read.delim(paste0(txt_path,"subjID.txt"), head=FALSE)
condition <- read.delim(paste0(txt_path,"group.txt"), head=FALSE)
KG_bl <- read.delim(paste0(txt_path,"KG_bl.txt"), head=FALSE)
KG_fu <- read.delim(paste0(txt_path,"KG_fu.txt"), head=FALSE)
KG_fu2 <- read.delim(paste0(txt_path,"KG_fu2.txt"), head=FALSE)
IG_bl <- read.delim(paste0(txt_path,"IG_bl.txt"), head=FALSE)
IG_fu <- read.delim(paste0(txt_path,"IG_fu.txt"), head=FALSE)
IG_fu2 <- read.delim(paste0(txt_path,"IG_fu2.txt"), head=FALSE)
measurement <- c(1:nrow(ID))
dmf <- data.frame(measurement,ID,condition,KG_bl,KG_fu,KG_fu2,IG_bl,IG_fu,IG_fu2)
colnames(dmf) <- c("measurement","ID","condition","Nbl","Nfu","Nfu2","Bbl","Bfu","Bfu2")

@@

<!-- Brain mask: Group*Time Interaction -->
There was no interaction of group and time point regarding the resting state connectivity for neither the PCC nor the NAcc as was hypothesized. Nor was there a significant main effect for any of the covariates of interest (time, group) in voxelwise inference with FDR correction. Results obtained for parametric estimation and non-parametric wild bootstrap did not differ.
When reducing the number of nuisance covariates by leaving out mean FD, connectivity was found between the PCC with one other voxel. In the connectivity maps only corrected with AROMA-CC co-activation of voxel $x,y,z = 18,42,30$ [mm] yielded $Z = 4.72$ ($q_{FDRcorr} = 0.040$). However, verification of the effect with non-parametric bootstrapping failed to yield significant ($p_{\mathrm{FWEcorr}} = 0.061$; $q_{FDRcorr} = 0.999$)<!-- but FWE-corr sig?!, ich bin mir nicht ganz sicher, ob wir das überhaupt erwähnen wollen ... -->.
There was no other significant co-activation for any other region of interest for neither of the preprocessing variants.

<!-- GM mask: Group*Time Interaction -->
Parametric and non-parametric significance test for the model testing for group-time-interaction did not show any different results when using a grey matter mask. Again, parametric estimation and non-parametric estimation differed in regard to the group-time-interaction of PCC and voxel ($18,42,30$) in the connectivity maps without GSR correction. While co-activation was significant in parametric estimation ($Z = 4.72$, $q_{FDRcorr} = 0.040$), it was non-significant when using wild bootstrap ($q_{\mathrm{FDRcorr}} = 0.998$)<!-- also FWE-corr n.s -->.

@@

<!-- SUPPORT OF ORIGINAL HYPOTHESIS -->
<!-- false positive -->
To summarize, there were few significant co-activation that emerged from the marginal models. Co-activation was locally highly specific and (NOT???) in accordance with our hypothesis regarding network activity changes. Given the multiplicity of of models resulting from variations of inspected networks and sensitivity analysis for different preprocessing and correction approached, the obtained significant correlations between seed regions and voxels are likely to be false positive. Ventures to verify effects by re-calculating with non-parametric Wild bootstrap confirmed supported presumption as effects were not robust across estimation procedures.

>>>>

# [ ] Evaluate SPM model comparison (more activation in SPM..)
# [ ] Discussion
# [ ] hervorheben, was von Präregistrierung abweicht
# [ ] brain images mit nilearn plotting tools einbinden
# [ ] Upload auf Neurovolt, cf. cobidas reporting guidelines
# [ ] re-do analysis with new sample 
# [ ] repeat analysis with exclusion of 10% of worst data
# [ ] Network tests

@@

dfw <- tidyr::pivot_wider(data = final,
                          id_cols = c("subj.ID","condition","Sex","Age_BL"),
                          names_from = "tp",
                          values_from = c("BMI","meanFD"))
```
```{r tabsample, echo=FALSE}
tab_sample <-
  knitr::kable(
    tab_sample,
    row.names = TRUE,
    format = "latex",
    booktabs = T,
    caption = "Distribution of data points at months after intervention")
tab_sample
```

@@

# table for descriptive statistics
descr <- psych::describeBy(dfw[,5:ncol(dfw)], group=dfw$condition,mat=T)
descr$predictor <- c(rep("BMI",6),rep("meanFD",6))
descr$tp <- car::recode(descr$vars, "c(1,4)='fu2';c(2,5)='fu';c(3,6)='bl'")
descr$group <- descr$group1
descr <- descr[,c("predictor","tp","group","n","mean","sd")]
descr <- descr[with(descr, order(predictor, tp)),]
descr[,c("mean","sd")] <- round(descr[,c("mean","sd")],2)
descr[c(2:6,8:12),"predictor"] <- ""
descr[c(2,4,6,8,10,12),"tp"] <- ""
rownames(descr) <- NULL

@@

ID <- read.delim(paste0(txt_path,"subjID.txt"), head=FALSE)
condition <- read.delim(paste0(txt_path,"group.txt"), head=FALSE)
KG_bl <- read.delim(paste0(txt_path,"KG_bl.txt"), head=FALSE)
KG_fu <- read.delim(paste0(txt_path,"KG_fu.txt"), head=FALSE)
KG_fu2 <- read.delim(paste0(txt_path,"KG_fu2.txt"), head=FALSE)
IG_bl <- read.delim(paste0(txt_path,"IG_bl.txt"), head=FALSE)
IG_fu <- read.delim(paste0(txt_path,"IG_fu.txt"), head=FALSE)
IG_fu2 <- read.delim(paste0(txt_path,"IG_fu2.txt"), head=FALSE)
measurement <- c(1:nrow(ID))
dmf <- data.frame(measurement,ID,condition,KG_bl,KG_fu,KG_fu2,IG_bl,IG_fu,IG_fu2)
colnames(dmf) <- c("measurement","ID","condition","N0","N6","N12","B0","B6","B12")

@@

<!-- Brain mask: Group*Time Interaction [CORRECTED] -->
There was no interaction of group and time point regarding the resting state connectivity for neither the PCC nor the NAcc as was hypothesized. Nor was there a significant main effect for any of the covariates of interest (time, group) in clusterwise inference with FWE correction.
Similarly, there were only non-findings when reducing the number of nuisance covariates by leaving out mean FD, no connectivity was found between the PCC with one other voxel.
Results did not differ between analyses of connetivity maps from different preprocessing pipelines.
<!-- There was no other significant co-activation for any other region of interest for neither of the preprocessing variants. -->

<!-- GM mask: Group*Time Interaction [OLD] -->
Parametric and non-parametric significance test for the model testing for group-time-interaction did not show any different results when using a grey matter mask. Again, parametric estimation and non-parametric estimation differed in regard to the group-time-interaction of PCC and voxel ($18,42,30$) in the connectivity maps without GSR correction. While co-activation was significant in parametric estimation ($Z = 4.72$, $q_{FDRcorr} = 0.040$), it was non-significant when using wild bootstrap ($q_{\mathrm{FDRcorr}} = 0.998$)<!-- also FWE-corr n.s -->.

@@

<!-- SUPPORT OF ORIGINAL HYPOTHESIS -->
<!-- false positive -->
To summarize, there were few significant co-activation that emerged from the marginal models. Co-activation was locally highly specific and (NOT???) in accordance with our hypothesis regarding network activity changes. Given the multiplicity of of models resulting from variations of inspected networks and sensitivity analysis for different preprocessing and correction approached, the obtained significant correlations between seed regions and voxels are likely to be false positive. Ventures to verify effects by re-calculating with non-parametric Wild bootstrap confirmed supported presumption as effects were not robust across estimation procedures.
<!-- limitations -->
Without an a priori power analysis it is not possible to determine if there is no effect or 
To clarify, extended considerations should be made to use a priori power analysis (e.g. with fMRIpower) or check evidence of absence with alternative
